Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Indent equations
Indent equation and make past tense
Fix ref

    \caption{Mean rotor power (left) and drag (right) coefficient curves from
        the tow tank experiments\cite{Bachant2015-RVAT-Re-dep-data}.}

@@

Turbulence kinetic energy profiles are also shown in
Figure~\ref{fig:br-cfd-profiles}. The turbulence kinetic energy is calculated as
\begin{equation}
k = k_{\mathrm{RA}} + \frac{1}{2} \left(
\overline{U^\prime}^2 +
\overline{V^\prime}^2 +
\overline{W^\prime}^2 \right),
\label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ and $k_{\mathrm{RA}}$ is the kinetic energy
calculated by the turbulence model, which is zero for the SA model.

>>>>

    \caption{Mean rotor power (left) and drag (right) coefficient curves from
        the tow tank experiments\cite{Bachant2016-RVAT-Re-dep}.}

@@

Turbulence kinetic energy profiles are also shown in
Figure~\ref{fig:br-cfd-profiles}. The turbulence kinetic energy was calculated as
\begin{equation}
    k = k_{\mathrm{RA}} + \frac{1}{2} \left(
    \overline{U^\prime}^2 +
    \overline{V^\prime}^2 +
    \overline{W^\prime}^2 \right),
    \label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ and $k_{\mathrm{RA}}$ is the kinetic energy
calculated by the turbulence model, which is zero for the SA model.
